Can money buy happiness?

### 2022-04-28 draft2.Rmd

@@

Cat's graph(s):

> This graph simply presents reported happiness level against the average weekly hours worked.The data comes from a study on healthy lifestyle elements such as sunshine hours in each place, price of a bottle of water, and ________. Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large. We wanted to see how hours worked We speculated that fewer weekly work hours would correlate to a greater happiness level, and the graph presents a loose trend that backs our speculations. The city with the fewest working hours (Copenhagen) reports a happiness level of 7.64. Though this is not the highest happiness level (that would be Helsinki), it is significantly higher than, say, Hong Kong where the work hours are around 41.7, on average paired, with a happiness level of 5.51. We recognize that there are cultural, political, and societal factors that could affect this rating.

```{r}

@@

  #mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%

@@

  theme_foundation() +
  theme(legend.title=element_blank())+
  theme(legend.background = element_blank())

```

```{r}
ggplotly(Healthy,
         tooltip = c("text",
                     "y",
                     "x",
                     "City")) %>% 
  layout(title = list(text = paste0('Is there a correlation between weekly work hours and happiness levels?',
                                    '<br>',
                                    '<sup>',
                                    'Graph by Cat Terres, data sourced from Kaggle ____ and _____',
                                    '</sup>')))
```

>>>>

> Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**. We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC. We wondered if countries with a higher GDPPC would be more unhappy reflecting that they may work longer hours in order to have such a high level of production. It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.

@@

> “I think that this is ultimately why we want money: It's to create a world that you prefer." -Hank Green

> This graph simply presents reported happiness level against the average weekly hours worked. Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large. It is easy to assume that those who work less have more time for leisure activities and maintenance of their well-being, and in turn we speculated that fewer weekly work hours would correlate to a greater happiness level. However, this graph does not present a strong enough trend to support our hypothesis. There is a loose trend, and this can help to give direction to our investigation despite not proving anything for a fact. What we DO learn from this graph is the complexity of happiness as a variable. Happiness is not only contingent on working hours, but factors such as higher average wages, government investment in citizens and their communities, and access to community resources. We recognize that there are cultural, political, and societal nuances that influence whether people work more or less and that different places have different attitudes surrounding work and money.

```{r, fig.width=5, }

@@

@@

  theme_foundation() +
  theme(legend.title=element_blank())+
  theme(legend.background = element_blank()) +
  theme(legend.position = "none")

ggplotly(Healthy,
         tooltip = c("text",
                     "y",
                     "x",
                     "City")) %>% 
  layout(title = list(text = paste0('Is there a correlation between weekly work hours and happiness levels?',
                                    '<br>',
                                    '<sup>',
                                    'Graph by Cat Terres, data sourced from Kaggle and World Population Review',
                                    '</sup>')))
```

#GDPPC vs. Hours Worked (Can we observe a relationship between the GDPC of each contry and the average amount of hours people work per week?) Can the observable patterns tell us something about the contries with low GDPC and a higher number of working hours? How can we relate this to happiness?

```{r}
country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
    col_types = cols(GDPM = col_number(), 
        GDP = col_number(), pop = col_number(), 
        GDPPC = col_number()))

healthy_data_2 <- healthy_data_dollars %>% 
  left_join(country_GDP,
            by = c("City" = "city"))

options(scipen=999)

GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
  geom_point() +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightblue",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))
